Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-07-26 Thesis/chapter/03-theoretical-background.tex
learning from data 1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment}
In two cases a deliberate design of experiment makes sense. 
If the query of a new data point is very expensive it favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
Continuous state spaces must be accommodated by arbitrary discretization.
\cite{cohn1996neural}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Linear Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AI vs statistics}
General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
\begin{enumerate}
	\item State the problem 
	\item Formulate the hypothesis
	\item Design the experiment/generate the data
	\item Collect the data and perform preprocessing
	\item Estimate the model 
	\item Interpret the model/draw the conclusions
\end{enumerate}
\textbf{1. Statement of the Problem} There was no clear statement of the problem. Now I would formulate it: "How to produce most insulating layer with least energy? How do we define most insulating?" That's why there are two output variables rather than one.
\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
\textbf{3. Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting. The data collection can affect the sampling distribution and influence the next steps. 
\textbf{4. Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection. Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task. Feature selection: A small number of informative features make the task of estimating dependencies easier. 
\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables.

There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
Issues of methods for learning from data: 
\begin{itemize}
	\item How to incorporate a priori assumptions into learning? 
	\item How to measure model complexity (i.e. flexibility to fit the training data)?
	\item How to find a optimal balance between the data and a priori knowledge? 
\end{itemize}

\cite{cherkassky1998learning}
%%
\td{let GPT-3 write}
check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
\url{https://journals.sagepub.com/doi/pdf/10.1177/1352458520978648}
\url{https://journals.sagepub.com/doi/full/10.1177/1352458520978648}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment}
In two cases a deliberate design of experiment makes sense. 
If the query of a new data point is very expensive it favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
Continuous state spaces must be accommodated by arbitrary discretization.
\cite{cohn1996neural}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Linear Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AI vs statistics}
\begin{itemize}
	\item \td{let GPT-3 write}
	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
	\item 
		\href
		{https://doi.org/10.1177\%2F1352458520978648}
		{Machine and deep learning in MS research are just powerful statistics – No}
\end{itemize}

\subsubsection{Learning from Data}
General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
\begin{enumerate}
	\item State the problem 
	\item Formulate the hypothesis
	\item Design the experiment/generate the data
	\item Collect the data and perform preprocessing
	\item Estimate the model 
	\item Interpret the model/draw the conclusions
\end{enumerate}
\textbf{1. Statement of the Problem} There was no clear statement of the problem. Now I would formulate it: "How to produce most insulating layer with least energy? How do we define most insulating?" That's why there are two output variables rather than one.
\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
\textbf{3. Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting. The data collection can affect the sampling distribution and influence the next steps. 
\textbf{4. Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection. Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task. Feature selection: A small number of informative features make the task of estimating dependencies easier. 
\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables. 
\cite{cherkassky1998learning}

There are not only \textbf{x}(input) and y(output) variables, but also \textbf{z}(uncontrolled/unobserved input variables).
Issues of methods for learning from data: 
\begin{itemize}
	\item How to incorporate a priori assumptions into learning? 
	\item How to measure model complexity (i.e. flexibility to fit the training data)?
	\item How to find a optimal balance between the data and a priori knowledge? 
\end{itemize}
\cite{cherkassky1998learning}

"Learning is the process of estimating an unkown (input,output) dependency of structure of a system using a limit number of observations."\cite{cherkassky1998learning}

The process informal part of selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} (page 25)

"Do not attempt to solve a specified problem by indirectly solving a harder general problem as an intermediate step."\cite{cherkassky1998learning}(p33)

"This approach works well only when the number of training samples is large relative to the (prespecified) model complexity (or the number of free parameters)".\cite{cherkassky1998learning}(p41)

Modeling bias in statistics is the discrepancy of the mismatch between parametric assumptions and the true dependency.
Modeling bias is overcome by using very flexible approximation function, with the tradeoff of more complex inductive (learning) steps.

Any learning process requires the following(p40): 
\begin{itemize}
	\item A (wide, flexible) set of approximating functions $\mathbf{f}(\mathbf{x},\omega),\; \omega \in \Omega$
	\item A priori knowledge to impose contrains
	\item An inductive principle (what needs to be done)
		\begin{itemize}
			\item penalizeation (regularization) inductive principle
			\item early stopping rules (with ANN, difficult to control and interpret)
			\item structural risk minimization (SRM) (order according to complexity)
			\item Bayesian Inference (add subjectivity to learning machine)
			\item Minimum Description Length (MDL, cryptic complicated uninteresting)
		\end{itemize}
	\item A learning method (how does it need to be done,implementation)
\end{itemize}

\textbf{Curse and Complexity of Dimensionality}
goal is to estimate function with finite samples, so it's always inaccurate (biased). 
meaning full estimate only possible with high sampling density, which is difficult for high dimensional functions.
\begin{enumerate}
	\item Sample sizes yielding the same denisty increse exponentially with dimension .
	\item A large radius is needed to enclose a fraction of the data points in a high-dimensional space.
	\item Almost every point is closer to an edge than to another point.
	\item Almost every point  is an outlier in its own projection.
\end{enumerate}

%%
Further Literature: 
\begin{itemize}
	\item 
		\href
		{https://doi.org/10.1016/0893-6080(94)90066-3}
		{Pedagogical pattern selection strategies}
	\item 
		\href
		{https://doi.org/10.1016/0893-6080(95)00137-9}
		{Neural Network Exploration Using Optimal Experiment Design}
	\item 
		\href
		{https://doi.org/10.1016/S0076-5392(08)63235-X} 
		{Chapter 6 Experiment Design}
	\item 
		\href
		{https://doi.org/10.1177\%2F1352458520978648}
		{Machine and deep learning in MS research are just powerful statistics – No}
\end{itemize}

### 2022-07-26 Thesis/chapter/06-results-and-discussion.tex
OED/DOE source found
learning from data 1

@@

\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
could have been verhindert durch lesen the docu and more papers more thoughoughly. 
Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
\subsection{XRD}

\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra}
	\label{fig:xrd}
\end{figure}

\td{I wanted to exhaust the possibilities of EA (not having enough data). i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{XRD}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra}
	\label{fig:xrd}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SEM}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I and PSO//Optimization}
\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}
\td{too much data as input, dimensionality reduction (PCA) and optimization}

@@

\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
could have been verhindert durch lesen the docu and more papers more thoughoughly. 
Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
\td{I wanted to exhaust the possibilities of EA (not having enough data). i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}

\td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
